Block bootstrap consistency\\under weak assumptions

### 2017-03-14 Paper.tex
[#40/check] Fix small error in matching bracket sizes

The assumption on the dispersion of the individual means,
$(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
\citepos{GoJ:03} under their additional requirement that the
expected block length be $o(\sqrt{n})$. When
the blocks are larger than $o(\sqrt{n})$, a case that \citet{GoW:02}
and \citet{GoJ:03} do not consider, the dispersion must be smaller
than they require.
To see these implications of this assumption, it is helpful to
consider a simple example: a stochastic process with a single break of
size $\Delta_n$ at time $T_n$:
\begin{equation*}
\mu_{nt} =
\begin{cases}
  \mu & \text{if } t \leq T_n \\
  \mu + \Delta_n & \text{otherwise}.
\end{cases}
\end{equation*}
A small amount of algebra gives the relationship,
\begin{equation*}
  \sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  = T_n (n - T_n) \Delta_n^2 / n \equiv D_n;
\end{equation*}
we have introduced $D_n$ to minimize notation in the subsequent
discussion.  For the Moving and Circular Block Bootstraps,
Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
the same relationship must hold for the expected block length for the
Stationary Bootstrap. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
some constants $\Delta_0$ and $\pi$ and for all $n$, then
$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
there is a break large enough that $\pi$ could be precisely
estimated \citep[as in][]{Bai:94}, but the break is ignored and the
bootstrap is applied to the entire dataset.

To see when Theorem~\ref{T1}'s Assumption~2 is satisfied, consider two
other parametrizations of this DGP\@. First, let $\Delta_n = \Delta_0$
and $T_n = T_0$ for some finite $T_0$. This mimics a setting where a
researcher intends to apply the bootstrap to a post-break sample, but
mistakenly includes a small number of pre-break observations as
well. In this case, Assumption 2 holds as long as
$M_n = o(\sqrt{n})$.  Similarly, suppose
$\Delta_n = \Delta / \sqrt{n}$ and $T_n = \pi n$, which mimics a
setting with a moderate break with unknown timing.  Then
$D_n \approx \Delta c (1 - c)$ and Assumption 2 again holds as long as
$M_n = o(\sqrt{n})$. Consequently, using block sizes of length
$o(\sqrt{n})$ ensures that Theorem 1's assumptions on the dispersion
of the $\mu_{nt}$ hold when there is a moderate amount of
heterogeneity---either because the sample is chosen to lie after a
large break estimated break or because any breaks are smaller in
magnitude and, consequently, potentially difficult to detect. When the
degree of heterogeneity is very small or nonexistent, so
$\sum_t (\mu_{nt} - \bar \mu_n)^2$ grows even slower, then larger
block lengths can also satisfy this condition.

>>>>

The assumption on the dispersion of the individual means,
$(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
\citepos{GoJ:03} under their additional requirement that the
expected block length be $o(\sqrt{n})$. When
the blocks are larger than $o(\sqrt{n})$, a case that \citet{GoW:02}
and \citet{GoJ:03} do not consider, the dispersion must be smaller
than they require.
To see these implications of this assumption, it is helpful to
consider a simple example: a stochastic process with a single break of
size $\Delta_n$ at time $T_n$:
\begin{equation*}
\mu_{nt} =
\begin{cases}
  \mu & \text{if } t \leq T_n \\
  \mu + \Delta_n & \text{otherwise}.
\end{cases}
\end{equation*}
A small amount of algebra gives the relationship,
\begin{equation*}
  \sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  = T_n (n - T_n) \Delta_n^2 / n \equiv D_n;
\end{equation*}
we have introduced $D_n$ to minimize notation in the subsequent
discussion.  For the Moving and Circular Block Bootstraps,
Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
the same relationship must hold for the expected block length for the
Stationary Bootstrap. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
some constants $\Delta_0$ and $\pi$ and for all $n$, then
$D_n \approx \Delta_0^2 \, \pi (1 - \pi) \, n$ and Assumption~2 fails to
hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
there is a break large enough that $\pi$ could be precisely
estimated \citep[as in][]{Bai:94}, but the break is ignored and the
bootstrap is applied to the entire dataset.

To see when Theorem~\ref{T1}'s Assumption~2 is satisfied, consider two
other parametrizations of this DGP\@. First, let $\Delta_n = \Delta_0$
and $T_n = T_0$ for some finite $T_0$. This mimics a setting where a
researcher intends to apply the bootstrap to a post-break sample, but
mistakenly includes a small number of pre-break observations as
well. In this case, Assumption 2 holds as long as
$M_n = o(\sqrt{n})$.  Similarly, suppose
$\Delta_n = \Delta / \sqrt{n}$ and $T_n = \pi n$, which mimics a
setting with a moderate break with unknown timing.  Then
$D_n \approx \Delta \pi (1 - \pi)$ and Assumption 2 again holds as long as
$M_n = o(\sqrt{n})$. Consequently, using block sizes of length
$o(\sqrt{n})$ ensures that Theorem 1's assumptions on the dispersion
of the $\mu_{nt}$ hold when there is a moderate amount of
heterogeneity---either because the sample is chosen to lie after a
large break estimated break or because any breaks are smaller in
magnitude and, consequently, potentially difficult to detect. When the
degree of heterogeneity is very small or nonexistent, so
$\sum_t (\mu_{nt} - \bar \mu_n)^2$ grows even slower, then larger
block lengths can also satisfy this condition.
